---
title: "Lab 08 - Quantifying Uncertainty"
author: "Catherine O'Reilly"
date: "4/27/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(tidymodels)
library(lubridate)
```

## Exercises

### Exercise 1

The name of the file we need to load is us-mms-simple.csv and it is a csv file.

```{r import-data}
fluxes <- read_csv("data/us-mms-simple.csv")
```

## Fix dates

```{r fix-dates, eval = F}
fluxes <- fluxes %>% 
  mutate(date = mdy_hm(date))
head(fluxes)
```

### Exercise 2

-   Then, complete the pipeline so that it will subset the data for **one month in summer in 2020** (June, July or August).\

-   Then, select a numerical variable you found to be interesting in Lab 7 (or another numerical variable you find interesting).

-   Remember to change `eval` to `T` when you are ready to run the chunk.
    Note that you are creating a new data frame called `fluxes_subset` from this pipeline.

```{r subset-fluxes, eval = T}
fluxes_subset <- fluxes %>% 
  filter(date > "2020-06-01" & date < "2020-06-30") %>% 
  select(date, fco2, evaporation)
head(fluxes_subset, 10) 
```

### Exercise 3

3.  Before we generate many random samples from our month of flux data. Let's double check the dimensions of our dataset.

-   Insert and label a code chunk into your starter file under Exercise 3 or use in-line code to state how many observations (rows) of data you have for the month you selected.
-   Also state what each row represents

``` {r counting number of rows}
nrow(fluxes_subset)
```
There are 695 observations in June 2020, with each row representing a specific hour of a day.

### Exercise 4

4.  If we defined our underlying population as **summertime** `fco2` fluxes, would our sample be a good sample of that population? Explain why or why not?

Defining our underlying population as summertime, the month of June (the sample I have chosen) would likely be a good representative of that population. Because fco2 fluxes vary drastically across the seasons, the month of June would not be a good representative of the entire year-round fco2 fluxes, but because we are defining the overall population as just the summertime season, the month of June would be a good sample. 

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.

### Exercise 11

Remove this text, and add your answer for Exercise 11 here.

### Exercise 12

Remove this text, and add your answer for Exercise 12 here.

### Exercise 13

Remove this text, and add your answer for Exercise 13 here.

